Exploring_symptoms_across_cohorts

### 2022-10-27 characterisation/Code/Comparing_symptoms.Rmd
update

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning=FALSE, 
                      message=FALSE, 
                      comment = FALSE,
                      cache.lazy=FALSE)
options(scipen=999)
```

```{r include=FALSE}
# packages
library(SqlRender)
library(DBI)
library(DatabaseConnector)
library(here)
library(dplyr)
library(tidyr)
library(CDMConnector)
library(stringr)
library(lubridate)
library(gtsummary)
library(tableone)

@@

# get data for table 1
 table1_data_new_infections  <- load(here("data", "table1_data_new_infections.Rda")))

@@

```{r}

table1.data<-rbind(  
# those without missing values
       table1_data_new_infections   %>%
        mutate(group = "With COVID-19_infection"),
        table1_data_new_infections  %>%
        filter(long_covid == 1)%>%
          mutate(group = "90 days Long Covid symtpoms"))

@@

# format numbers (eg commas etc)  
# functionality does not seem to be in tableone package
# so do this manually
for(i in 1:2) {
# tidy up 
  cur_column <- summary.characteristics[, i]
  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
                as.numeric() 
  cur_column <-nice.num(cur_column)
  # add back in
  summary.characteristics[, i] <- str_replace(string=summary.characteristics.loss[, i], 
                              pattern='[0-9.]+\\b', 
                              replacement=cur_column)    
}

@@

```{r}

table  <- tbl_merge(tbls = list(t.covid.infection,      
                                t.covid.reinfections,
                                t.tested.negative.earliest,
                                t.pcr.negative.earliest
                                 ), 
                     tab_spanner = c("", "", "", ""))

@@

```
```{r}
## explorar numero de sintomas en tested negative y covid infection
# plot_grid(
#   covid_infection_numb_symp %>% filter(window==90) %>% 
#     ggplot(aes(all_symp)) +geom_bar() + theme_minimal() + ggtitle("Covid-19")  ,
# tested_negative_all_numb_symp %>% filter(window==90) %>%
#   ggplot(aes(all_symp)) +geom_bar() + theme_minimal() + ggtitle("Tested negative")
# )

>>>>

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE,
                      warning=FALSE, 
                      message=FALSE, 
                      comment = FALSE,
                      cache.lazy=FALSE)
options(scipen=999)

```{r include=FALSE}
# packages
library(SqlRender)
library(DBI)
library(DatabaseConnector)
library(here)
library(dplyr)
library(tidyr)
library(CDMConnector)
library(stringr)
library(lubridate)
library(gtsummary)
library(tableone)
library(kableExtra)

@@

# get data for table 1
load(here("data", "table1_data_new_infections.Rda"))

@@

```{r include=FALSE}
table1.data<-rbind(  
# those without missing values
       table1_data_new_infections   %>%
        mutate(group = "COVID-19_infection"),
        table1_data_new_infections  %>%
        filter(long_covid == 1)%>%
          mutate(group = "Long Covid symptoms (90 days)"))

@@

## Table: Baseline characteristics of individuals with COVID-19 and with long COVID-19 
```{r}

kable(summary.characteristics, 
      col.names = c("New COVID-19 infection",  
                    "Long COVID-19, 90 days",
                    "SMD"
                    ))%>%
  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
 # pack_rows("Baseline comorbidities", 40, 44)

@@

## Table: Symptoms distribution across cohorts

```{r}
table  <- tbl_merge(tbls = list(t.covid.infection,   
                                t.covid.confirmed,
                                t.covid.reinfections,
                                t.tested.negative.earliest,
                                t.pcr.negative.earliest
                                 ), 
                     tab_spanner = c("","", "", "", ""))

@@
